Astr 513: Final Project

### 2016-05-07 Final_Project/ms.tex
Removed some clutter. Rearranged todo notes to be in the proper places.

\section{Results}
\label{sec:results}
\TM{Discuss the results and show the corner plots. Example plot included.
  We should have one corner plot without priors and one with priors.}
%\LC{Not sure where to put why we couldn't do the full analysis of Rest's data. 
%  I'm putting it here for now.}
%A complete analysis using the data from \citet{rest2014} is not done 
%in our paper since there are several issues with the publicly released 
%data. It is not apparent which uncertainties belonged to the statistical 
%covariance matrix since only the systematic covariance matrix is clearly 
%presented. Moreover, intrinsic dispersion of the data and photometric errors 
%of the distances depend on nuisance parameters in addition to the covariances 
%between the fit parameters. Fine-tuning nuisance parameters places a significant 
%time restraint on our work and is beyond the scope of this paper. For these reasons, 
%we only present the results for \citet{rest2014} that do not include the priors 
%from \citet{planck2013}.

\EW{Filler table for the lambda CDM fits}
\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & 0      & 0 \\
    Betoule et al. (no priors) & 0      & 0 \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & 0      & 0 \\
    \end{tabular}
    \caption {\label{tab:lcdm}Posterior distirbutions of parameters in the
      $\Lambda$CDM model. uncertainties denote symmetrized 68\%
      confidence intervals maginalized over other parameters.}
\end{table}

\EW{Just a filler for the table for the wCDM fits}
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \Planck likelihood only    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distirbutions of parameters in the
    wCDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals maginalized over other parameters.}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data without including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}
%
\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}

>>>>

\section{Results}
\label{sec:results}
%\LC{Not sure where to put why we couldn't do the full analysis of Rest's data. 
%  I'm putting it here for now.}
%A complete analysis using the data from \citet{rest2014} is not done 
%in our paper since there are several issues with the publicly released 
%data. It is not apparent which uncertainties belonged to the statistical 
%covariance matrix since only the systematic covariance matrix is clearly 
%presented. Moreover, intrinsic dispersion of the data and photometric errors 
%of the distances depend on nuisance parameters in addition to the covariances 
%between the fit parameters. Fine-tuning nuisance parameters places a significant 
%time restraint on our work and is beyond the scope of this paper. For these reasons, 
%we only present the results for \citet{rest2014} that do not include the priors 
%from \citet{planck2013}.

\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & 0      & 0 \\
    Betoule et al. (no priors) & 0      & 0 \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & 0      & 0 \\
    \end{tabular}
    \caption {\label{tab:lcdm}Posterior distirbutions of parameters in the
      $\Lambda$CDM model. uncertainties denote symmetrized 68\%
      confidence intervals maginalized over other parameters.
      \EW{Filler table for the lambda CDM fits}}
\end{table}
%
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \Planck likelihood only    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distirbutions of parameters in the
    wCDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals maginalized over other parameters.
    \EW{Just a filler for the table for the wCDM fits}}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data without including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}
%
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}
